Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2019-11-07 manuscript/climate_sensitivity_draft.Rmd
update height change

Crown positions were recorded in the field during the growing season of 2018 following the crown position protocol of @jennings_assessing_1999, whereby positions were ranked as dominant, codominant, intermediate, or suppressed. As there was no way to retroactively estimate crown position, we assumed that 2018 crown position was reflective of each tree's position over the past 60 years. *While some trees undoubtedly changed position, an analysis of crown position relative to height (Fig. 2) and height change since the beginning of the study period indicated that change was likely slow. Specifically, average tree height growth was confined to <0.5m from 1966 to 1977, and ~1m from 1977 to 1999.* (see issue [#60](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/60)).

>>>>

Crown positions were recorded in the field during the growing season of 2018 following the crown position protocol of @jennings_assessing_1999, whereby positions were ranked as dominant, codominant, intermediate, or suppressed. As there was no way to retroactively estimate crown position, we assumed that 2018 crown position was reflective of each tree's position over the past 60 years. While some trees undoubtedly changed position, an analysis of crown position relative to height (Fig. 2) and height change since the beginning of the study period indicated that change was likely slow (Fig. S3). Specifically, average tree height growth was confined to <0.5m from 1966 to 1977, ~1m from 1977 to 1999, and **# (IAN)** from 1999 to 2018.
